---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bbouretro

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/bbouretro/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/bbouretro/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/bbouretro/branch/main/graph/badge.svg?token=y99t6ttYNS)](https://app.codecov.io/gh/poissonconsulting/bbouretro?branch=main)
<!-- badges: end -->

## Introduction
The goal of bbouretro is to provide the ability to calculate survival, recruitment and population growth using the classical methods. 

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/bbouretro)

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/bbouretro")
```

or alternatively using pak

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("poissonconsulting/bbouretro")
```

## Example

```{r}
library(bbouretro)
library(bboudata)

# generate recruitment estimate for each year
recruitment_est <-
  bbr_recruitment(
    bbourecruit_c,
    pFemales = 0.65,
    sexratio = 0.5,
    variance = "binomial"
  )
bbr_plot_recruitment(recruitment_est)

# generate survival estimate for each year
survival_est <-
  bbr_km_survival(
    bbousurv_c,
    MortType = "Total",
    variance = "Pollock"
  )
bbr_plot_survival(survival_est)

# calculate lambda now that both recruitment and survival have been calculated
lambda_est <- bbr_lambda_sim(recruitment_est, survival_est)
summary <- bbr_lambda_summarize(lambda_est)
summary
bbr_plot_lambda(lambda_est)
bbr_plot_lambda_distributions(lambda_est, "C")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/bbouretro/issues).

[Pull requests](https://github.com/poissonconsulting/bbouretro/pulls) are always welcome.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
