---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- # Copyright 2024 Province of Alberta -->
<!-- # -->
<!-- # Licensed under the Apache License, Version 2.0 (the "License"); -->
<!-- # you may not use this file except in compliance with the License. -->
<!-- # You may obtain a copy of the License at -->
<!-- # -->
<!-- # http://www.apache.org/licenses/LICENSE-2.0 -->
<!-- # -->
<!-- # Unless required by applicable law or agreed to in writing, software -->
<!-- # distributed under the License is distributed on an "AS IS" BASIS, -->
<!-- # WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied. -->
<!-- # See the License for the specific language governing permissions and -->
<!-- # limitations under the License. -->

# bbouretro

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/bbouretro/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/bbouretro/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/bbouretro/branch/main/graph/badge.svg?token=y99t6ttYNS)](https://app.codecov.io/gh/poissonconsulting/bbouretro?branch=main)
<!-- badges: end -->

## Introduction
The goal of bbouretro is to provide the ability to calculate survival, recruitment and population growth using the classical methods. 

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/bbouretro)

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/bbouretro")
```

or alternatively using pak

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("poissonconsulting/bbouretro")
```

## Example

```{r}
set.seed(101)

library(bbouretro)
library(bboudata)

# generate recruitment estimate for each year
recruitment_est <-
  bbr_recruitment(
    bbourecruit_c,
    p_females = 0.65,
    sex_ratio = 0.5,
    variance = "bootstrap"
  )
bbr_plot_recruitment(recruitment_est)

# generate survival estimate for each year
survival_est <-
  bbr_survival(
    bbousurv_c,
    mort_type = "total",
    variance = "greenwood"
  )
bbr_plot_survival(survival_est)

# calculate lambda now that both recruitment and survival have been calculated
growth_est <- bbr_growth(recruitment_est, survival_est)
summary <- bbr_growth_summarize(growth_est)
summary
bbr_plot_growth(growth_est)
bbr_plot_growth_distributions(growth_est)
```

## bbou Suite

`bbouretro` is part of the bbou suite of tools. 
Other packages in this suite include:

- [bboudata](https://github.com/poissonconsulting/bboudata)
- [bboutools](https://github.com/poissonconsulting/bboutools)
- [bboushiny](https://github.com/poissonconsulting/bboushiny)
- [bbousims](https://github.com/poissonconsulting/bbousims)

## Contribution

Please report any [issues](https://github.com/poissonconsulting/bbouretro/issues).

[Pull requests](https://github.com/poissonconsulting/bbouretro/pulls) are always welcome.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
